\casesection{Simple channel flow}
\label{case:channelflow_simple}
\paragraph*{Purpose}
The purpose of this validation study is to show that for a schematised homogeneous channel, Delft3DFLOW
computes accurate water elevations, logarithmic velocity profiles in the vertical direction, and
parabolic vertical viscosity profiles. This validation study is performed for the $\sigma$-model. In addition, both
2D and 3D models are investigated, with both the algebraic and the \mbox{$k$-$\epsilon$} turbulence model. For the 3D
models, different vertical layer distributions are investigated. A tracer is also added to check conservation
of mass.

\paragraph*{Linked claims}
Claim \ref{cl:tidal}: test Accurate simulation of steady and unsteady flow.
Claim 2.4.1: Accurate, robust and computationally efficient algorithmic implementation.

\paragraph*{Approach}
Flow in a simple channel with sloping bathymetry is investigated. A steady solution is reached, in
which the vertical viscosity term balances the barotropic pressure gradient. For this steady situation
an analytical solution is available from the 2D shallow water equations. Results from Delft3D-FLOW
simulations are compared to the analytical solution. Both 2D and 3D simulations are performed. For 2D
simulations water depth and depth-averaged velocity are compared to the analytical solution and for
3D simulations also vertical profiles for velocity and eddy viscosity are investigated. In the latter case,
solutions are obtained with both the algebraic and the turbulence model. It is validated whether
both models produce logarithmic velocity profiles and parabolic eddy viscosity profiles. Also, a comparison
has been made between the $\sigma$-layer and with the Z-layer model results.

\paragraph*{Model description}
The properties of the model used in this validation

\paragraph*{Results}

\paragraph*{Conclusion}
\endinput
































\chapter{Templates}
\rule{\linewidth}{1pt}
Example claim:
\begin{verbatim}
\begin{claimlist}
\claim{\DFLOWFM\ can be used for an accurate prediction of the tidal
dynamics (water elevation, currents) in estuaries or coastal seas.}
\label{cl:tidal}
\substantiation Validation Study~\ref{case:channelflow_simple} (Simple channel flow); \\
Validation Study 3.2.6 (Numerical scale model of an estuary). \\
Validation Study 3.2.7 (Numerical scale model of an estuary and a tidal
lock).
Validation Study 3.4.1 (North Sea).
\references 
\end{claimlist}
\end{verbatim}

\rule{\linewidth}{1pt}
Example case:
\begin{verbatim}
\subsection{Simple channel flow}
\label{case:channelflow_simple}
\paragraph{Purpose}

\paragraph{Linked claims}
Claim \ref{cl:tidal}: test Accurate simulation of steady and unsteady flow.

\paragraph{Approach}

\paragraph{Model description}

\paragraph{Results}

\paragraph{Conclusion}
\end{verbatim}

\end{document}